%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{wasysym}
%\usepackage[misc]{ifsym}
\usepackage{marvosym}

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{KONSTANTIN GENIN\\\\ }% konstantin.genin@gmail.com \\ konstantingenin.com\\ } % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{Department of Philosophy \\ Carnegie Mellon University \\ 5000 Forbes Avenue Pittsburgh, PA 15213}  % Your address 1}

\address{\Letter \hspace{1pt} konstantin.genin@gmail.com \\ \Mobilefone \hspace{1pt} +1 718.637.1493 \\ \Mundus \hspace{1pt} konstantingenin.com \\ }
%\address{{\bf Permanent Address} \\ 5833 Hobart Street \\ Pittsburgh, PA 15217  \\ cell: +1 718.637.1493 }

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

%\section{\centerline{OBJECTIVE}}

%\vspace{8pt} % Gap between title and text

%A position in Personnel Administration utilizing skills in recruiting, training and compensation.\\ 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{8pt} % Gap between title and text

{\sl Doctor of Philosophy}, 
Logic, Computation and Methodology \hfill Expected 2017 \\ 
Department of Philosophy, Carnegie Mellon University 

{\sl Master of Science}, 
Logic, Computation and Methodology \hfill January 2015 \\ 
Department of Philosophy, Carnegie Mellon University  

 
{\sl Bachelors of Arts}, Mathematics and Philosophy \hfill May 2009 \\ 
Departments of Mathematics and Philosophy resp., Brown University 


%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PUBLICATIONS}} 

\vspace{8pt} % Gap between title and text

Konstantin Genin, Kevin T. Kelly. ``Learning, Theory Choice, and Belief Revision.'' Forthcoming in {\em Studia Logica}.

Kevin T. Kelly, Konstantin Genin, Hanti Lin ``Realism, Rhetoric, and Reliability.'' {\em Synthese} 193.4:  1191-1223, 2016.

Konstantin Genin, Kevin T. Kelly. ``Theory Choice, Theory Change, and Inductive Truth-Conduciveness.'' {\em Proceedings of the Fifteenth Conference on Theoretical Aspects of Rationality and Knowledge} (TARK), 2015.

Kevin T. Kelly, Konstantin Genin. ``Complexity, Ockham's Razor, and Truth.'' Collected in {\em Modes of Explanation: Affordances for Action and Prediction.} Lissack, Michael ed. Palgrave Macmillian, 2014.

Ryan Carlson, Konstantin Genin, Martina Rau, Richard Scheines. ``Student Profiling from Tutoring System Log Data: When do Multiple Graphical Representations Matter?'' {\em Proceedings of the Educational Data Mining (EDM) Conference}, 2013.

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{TALKS}}

\vspace{8pt} % Gap between title and text

``Deduction, Induction, Statistics and Topology'' (Kelly, Genin). \hfill November 2016\\
 Workshop in the Logical Structure of Correlated Information Change,\\ Amsterdam.

``A Topological Explanation of Empirical Simplicity'' (Kelly, Genin). \hfill November 2016\\
Philosophy of Science Association Meeting, \\
Altanta.

``Deduction, Induction, and Statistical Inference'' (Kelly, Genin). \hfill September 2016\\
Philosophy of Scientific Experimentation 5,\\
University of Belgrade.

``Simplicity and Scientific Questions'' (Genin). \hfill June 2016\\ 
Questions and Attitudes Workshop,\\
Carnegie Mellon Univeristy.

``Theory Choice, Theory Change, and Inductive Truth Conduciveness'' (Genin, Kelly).\\
\begin{enumerate}
\item Bristol-Gr\"{o}ningen Conference in Formal Epistemology,\\University of Bristol. \hfill July 2015
\item Conference on Theoretical Aspects of Rationality and Knowledge,\\ Carnegie Mellon. \hfill June 2015
\item Formal Epistemology Workshop,\\ University of Washington, St. Louis. \hfill May 2015
\item Fourth CSLI Workshop on Logic, Rationality, and Intelligent Interaction,\\ Stanford (Invited Talk). \hfill May 2015
\end{enumerate}

``A Topological Theory of Empirical Simplicity'' (Kelly, Genin, Lin). \hfill November 2014\\
Philosophy of Science Association Meeting,\\
Chicago.

``Learning with Ockham: Simplicity in Inductive Inference'' (Genin). \hfill October 2014\\
Cool Logic Seminar,\\ 
Institute for Logic, Language and Computation, Amsterdam.

``An Epistemic Justification of Ockham's Razor'' (Kelly, Genin) \hfill October 2014\\Rene Descartes Lectures,\\
Tilburg University.

``The St. Petersburgh Paradox'' (Genin, Heesen). \hfill July 2014\\
Swiss Institute Exhibition,\\ 
New York City. 

``Tracking and Statistical Knowledge'' (Genin). \hfill January 2014\\
 11th Annual Graduate Student Conference in Epistemology,\\
University of Miami. 

``Contraction and the Loss of True Belief'' (Shear, Genin).\\
\begin{enumerate}
\item North American Summer School in Logic, Language, and Information,\\ Univeristy of Maryland, College Park. \hfill June 2014
\item Canadian Society for History and Philosophy of Science Annual Meeting,\\ St. Catherine's, Ontario. \hfill May 2014
\item Association of Symbolic Logic North American Meeting,\\ University of Colorado, Boulder. \hfill May 2014
\item Colombian Conference in Logic, Epistemology and Philosophy of Science,\\ Universidad de Los Andes, Bogota. \hfill February 2014
\end{enumerate}
 (NASSLI), Univeristy of Maryland, College Park, June 2014. [slides]

Canadian Society for History and Philosophy of Science Annual Meeting (CSHPS), St. Catherines, Ontario, May 2014.

Association of Symbolic Logic North American Meeting, University of Colorado, Boulder, May 2014.

Columbian Conference in Logic, Epistemology and Philosophy of Science (Philogica III), Universidad de Los Andes, Bogota, Columbia, February 2014.

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PUBLICATIONS}} 

\vspace{15pt} % Gap between title and text
\begin{itemize} \itemsep -2pt % Reduce space between items
\item ``Job Analysis - A True Picture," Journal of Headhunters, Vol. 5, Number 3. Fall 1990 
\item ``The Fine Tuning of Interpersonal Skills," Journal of Recruiting/Hiring, Vol. 16, Number 7, August 1990
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{MEMBERSHIPS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
American Psychological Association, Student Affiliate \\
Vice President of Activities, RPI Weight-training Club \\ 
Chairperson, Entertainment Committee, Utica College \\ 
Latin-American Student Union, Utica College \\
Member All-American Nautilus 
\end{center}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{HONORS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Full tuition assistantship, Rensselaer Polytechnic Institute \\
PSI CHI National Honor Society \\
PHI THETA KAPPA National Honor Society 
\end{center}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERESTS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Classical piano, jazz, bodybuilding/aerobic exercise, cooking, dancing
\end{center} 

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}